Deployable Probabilistic Programming

### 2019-04-19 paper/paper.tex
insights prologue

In our journey towards implementation and release of Infergo,

@@

\begin{itemize}
	\item The Go parser and abstract syntax tree serializer are
		a part of the standard library. Parsing, transforming,
		and generating Go source code is straightforward and
		effortless.
	\item Type inference (or \textit{type checking} as it is
		called in the Go ecosystem), also provided in the
		standard library, augments parsing and allows to
		selectively apply transformation-based automatic
		differentiation  based on static expression types. 
	\item Go provides reflection capabilities for almost any aspect
		of the running program, without compromising efficiency.
		Reflection gives the flexibility highly desirable to
		implement features such as calling Go library
		functions from the model code.
	\item Go compiles and runs fast. Fast compilation and
		execution speeds allow to use the same facility for both
		exploratory design of probabilistic models and for
		inference in production environment.
	\item Go is available on many platforms and for a wide range
		of operating systems and environments, from portable
		devices to supercomputers. Go programs can be
		cross-compiled, and go programs can be reliably
		developed and deployed in heterogeneous environments.
	\item Go offers efficient parallel execution as a
		first-class feature, via so-called \textit{goroutines}.
		Goroutines streamline implementation of sampling-based
		inference algorithms. Sample generators and consumers
		are run in parallel, communicating through channels. 
		Inference is easy to parallelize in order to exploit
		hardware multi-processing, and samples are retrieved
		lazily for postprocessing. 
\end{itemize}

>>>>

In our journey towards implementation and deployment of Infergo, we
considered options and made implementation decisions which we
believe to have been crucial for addressing the challenges and
following the guidelines we formulated for implementation of a
deployable probabilistic programming facility. While different
choices may be as well suited for the purpose as the ones we
made, we feel it important to share our contemplations and
justify decisions, to which the rest of this section is
dedicated, from choosing the implementation language, through
details of automatic differentiation, to support for inference
on streaming and stochastic observations.

@@

\begin{itemize}
	\item The Go parser and abstract syntax tree serializer are
		a part of the standard library. Parsing, transforming,
		and generating Go source code is straightforward and
		effortless.
	\item Type inference (or \textit{type checking} as it is
		called in the Go ecosystem), also provided in the
		standard library, augments parsing and allows to
		selectively apply transformation-based automatic
		differentiation  based on static expression types. 
	\item Go provides reflection capabilities for almost any aspect
		of the running program, without compromising efficiency.
		Reflection gives the flexibility highly desirable to
		implement features such as calling Go library
		functions from the model code.
	\item Go compiles and runs fast. Fast compilation and
		execution speeds allow to use the same facility for both
		exploratory design of probabilistic models and for
		inference in production environment.
	\item Go is available on many platforms and for a wide range
		of operating systems and environments, from portable
		devices to supercomputers. Go programs can be
		cross-compiled, and Go programs can be reliably
		developed and deployed in heterogeneous environments.
	\item Go offers efficient parallel execution as a
		first-class feature, via so-called \textit{goroutines}.
		Goroutines streamline implementation of sampling-based
		inference algorithms. Sample generators and consumers
		are run in parallel, communicating through channels. 
		Inference is easy to parallelize in order to exploit
		hardware multi-processing, and samples are retrieved
		lazily for postprocessing. 
\end{itemize}
